In the last few years, most mobile games on the market are dominated by Free-to-Play（F2P）business models, which makes In-App Purchase（IAP）more and more important, and has become the focus of game developer operations. In order to be able to launch accurate marketing that successfully attracts all types of players, it is necessary for the data analysis team to conduct research on paying players, and hope to be able to successfully predict potential paying players in the new player group, so as to improve the willingness of IAP. Among the payer data, effective mining of data features and prediction through machine learning are goals of this research.

This paper proposes a big data mining framework for this topic. It will need to process the data and data analysis before prediction, then train and optimize the model via machine learning algorithm. Finally, analyze the feature importance with the prediction results. This framework will be composed of four major stages: (1) data pre-processing stage, (2) data analysis stage, (3) machine learning stage, (4) feature importance analysis stage.

According to the experimental results, with the big data mining framework we proposed, the valueless data was cleaned up by the observation period of valueless players, and the target values of payer and non-payer were prepared through the definition period of payer. The valuable player game play record is prepared by the mining period of data mining. Through Exploratory Data Analysis（EDA）, unreasonable data features and high-information data features are found to infer valuable data features. Through the prediction of the learning model, it can predict potential new paying players, and analyze the importance of features according to the prediction results, understand the player's consumption reasons and the connection with game. Overall, the framework will effectively reduce the time cost and labor cost of predicting paying players, and obtain favorable information for marketing.

Keywords: Purchases Prediction, Free-to-Play, Big Data, Data Mining, Machine Learning, Extreme Gradient Boosting